Analysing Constraint Grammars with a SAT-solver

### 2016-03-03 paper/lrec/eval_futurework.tex
change place of paragraph

\hline
              & 1 clitic & 2 clitics & readings only from the grammar \\ \hline
\# readings   & many     & more & \textless{}2000   \\ \hline
\# true 
   positives  & n   & m        & o    \\ \hline
\# false 
   positives  & p   & q        & super many    \\ \hline
\clock{}amb.
      classes & ??s              & ??min ??s    & ?h ??min  \\ \hline
\clock{}no amb.
      classes & ??s              & ??s          & ?min ??s  \\ \hline

@@

\paragraph{Full expressivity of CG-3}

In order to implement \textsc{substitute},
\textsc{add}, \textsc{addreading} and \textsc{map}, we need to be
prepared for new readings--even if the lexicon gives all readings that
exist in the lexicon, the user might give a nonexistent reading, or in
the case of MAP, a syntactic tag, which is (by definition) not in the
lexicon. A more scalable solution would be to make each tag a
variable, and ask the question ``can this reading be a noun? how about
singular? how about conditional?'' separately for each tag. Then we
could lift the restriction of tag combinations into a SAT solver: make
SAT clauses that prohibit a comparative to go with a verb, or
conditional with a noun.

@@

\paragraph{Support for grammar writers}
One additional feature is to suggest reformattings for a rule. Recall
figure~\ref{fig:regroup} from the introduction; in that case, the
original rule was written by the original author, and another
grammarian thought that the latter form is nicer to read. Doing the
reverse operation could also be possible. If a rule with long
disjunctions conflicts, it may be useful to split it into smaller
conditions, and eliminate one at a time, in order to find the
reason(s) for the conflict.

As for longer-term goals, we want to handle the full expressivity of CG-3,
with \textsc{map}, \textsc{add} and \textsc{substitute} rules, and
dependency structure. This also means finding different kinds of conflicts.
As soon as the tools are mature enough, we want to
evaluate them with actual grammar writers,
in comparison with a corpus-based method or machine learning.
Finally, if the method proves feasible for CG, we want
to try applying it to other grammar formalisms.

>>>>

\hline
              & 1 clitic & 2 clitics & readings only from the grammar \\ \hline
\# readings   & many     & more & lagom   \\ \hline
\# true 
   positives  & n   & m        & o    \\ \hline
\# false 
   positives  & p   & q        & super many    \\ \hline
\clock{}amb.
      classes & ??s              & ??min ??s    & ?h ??min  \\ \hline
\clock{}no amb.
      classes & ??s              & ??s          & ?min ??s  \\ \hline

@@

\paragraph{Full expressivity of CG-3}
As for longer-term goals, we want to handle the full expressivity of CG-3,
with \textsc{map}, \textsc{add},  \textsc{addreading} and
\textsc{substitute} rules, as well as dependency structure. 
This also means finding different kinds of conflicts.
In order to implement rules that may add new readings, or new tags to
existing readings, we need to modify our approach in the SAT-encoding.
Even if the lexicon gives all readings that exist in the lexicon, the
user might give a nonexistent reading, or in the case of MAP, a
syntactic tag, which is (by definition) not in the lexicon. A more
scalable solution would be to make each tag a variable, and ask the
question ``can this reading be a noun? how about singular? how about
conditional?'' separately for each tag. Then we could lift the
restriction of tag combinations into a SAT solver: make SAT clauses
that prohibit a comparative to go with a verb, or conditional with a noun.

@@

\paragraph{Support for grammar writers}
One additional feature is to suggest reformattings for a rule. Recall
figure~\ref{fig:regroup} from the introduction; in that case, the
original rule was written by the original author, and another
grammarian thought that the latter form is nicer to read. Doing the
reverse operation could also be possible. If a rule with long
disjunctions conflicts, it may be useful to split it into smaller
conditions, and eliminate one at a time, in order to find the
reason(s) for the conflict.
As soon as the tools are mature enough, we want to
evaluate them with actual grammar writers,
in comparison with a corpus-based method or machine learning.
Finally, if the method proves feasible for CG, we want
to try applying it to other grammar formalisms.
